Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2021-01-15 paper/paper.Rmd
remove a figure

```{r}
load("dispersal_kernels.RData")
```
## Seed dispersal distances and long distance dispersal

**Figure 3.**
```{r fig.width=6}
library(dplyr)
library(cowplot)

null_kernel <- null_dispersal %>% 
  ggplot(., aes(x = dispersal)) +
  geom_histogram(aes(y = ..density..))

indiv_kernel <- indiv_dispersal %>% 
  ggplot(., aes(x = dispersal)) +
  geom_histogram(aes(y = ..density..))

fam_kernel <- fam_dispersal %>% 
  ggplot(., aes(x = dispersal)) +
  geom_histogram(aes(y = ..density..))

plot_grid(null_kernel, indiv_kernel, fam_kernel, nrow = 3)

# Make the axis be the same length and beaks
# Remove redundant labels
# Test 3 rows or 3 columns
# Add red vertical line for LDD cutoff
# Include a zoom cut off for the tail

# plot_grid(
#   fam_dispersal %>%
#     ggplot(., aes(x = dispersal)) +
#     geom_histogram(),
#   plot_grid(fam_dispersion %>%
#             ggplot(., aes(y = mean_dispersal)) +
#             geom_boxplot(),
#           fam_dispersion %>%
#             ggplot(., aes(y = seed_dispersion)) +
#             geom_boxplot()), nrow = 2)
```

@@

**Figure 4.**
```{r fig.width=3, fig.height=5}

null_dispersion %>% 
  mutate(model = "Null") %>% 
  bind_rows(indiv_dispersion %>% 
              mutate(model = "Individual")) %>% 
  bind_rows(fam_dispersion %>% 
              mutate(model = "Family")) %>% 
  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) -> all_disp_data

all_disp_data %>% 
  ggplot(., aes(y = mean_xy_dispersal, x = model)) +
  geom_boxplot() -> dispersal_xy_box

all_disp_data %>% 
  ggplot(., aes(y = mean_dispersal, x = model)) +
  geom_boxplot() -> dispersal_box

all_disp_data %>% 
  ggplot(., aes(y = seed_dispersion, x = model)) +
  geom_boxplot() -> dispersion_box

plot_grid(dispersal_xy_box, dispersal_box, dispersion_box, nrow = 3)

# Edit redundant labels
# Fix names for axes

>>>>

## Seed dispersal distances and long distance dispersal

@@
